### 2013-06-04 doc/pgas13/flat-combining.tex
First draft of grappa,fc_shared_mem, and non_fc_stack

@@

@@

The flat combining framework transparently wraps the \emph{proxy} object. Behind this layer of indirection, the flat-combining framework manages multiple copies of the proxy so that, as discussed above, there is always at least one being committed and one to receive additional combining operations.

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figs/fc_shared_mem.pdf}
  \caption{Flat combining in shared memory. \TODO{walkthrough...}}
  \label{fig:fc_shared_mem}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figs/stack.pdf}
  \caption{\emph{GlobalStack in Grappa.} Each access must synchronize with the head node (blocking if another worker is performing an operation), put or get its value in the stack's storage, release the lock on the master, and finally continue.}
  \label{fig:stack}
\end{figure}

@@

The flat combining framework transparently wraps the \emph{proxy} object. Behind this layer of indirection, it manages multiple copies of the proxy so that, as discussed above, there is always at least one being committed and one to receive additional combining operations.
